A Survey Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
more little tweaks

\subsubsection{Wearables Scenarios}
%okay, this section is kind of confusing, I must admit..

We presented participants with scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first. All responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}. Questions were of the format, \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}. We created an initial pool of 292 questions by combining 73 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were:

@@

\subsubsection{Data Type}
Irrespective with whom the data was shared or on what device, participants were most concerned about photos/videos, especially if they contain embarrassment, nudity, or financial information. Information which can be used to impersonate the user (i.e. username and password for websites) and invasions of privacy (photos of someone at home) were also considered to be sensitive data. Top and bottom absolute <data> rankings can be seen in Tables ~\ref{top10} and ~\ref{bottom10}. {\color{red} should I say anything about the full list of 74 data types?}

>>>>

\subsubsection{Wearables Scenarios}
We presented participants with scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first. All responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}. Questions were of the format, \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}. We created an initial pool of 292 questions by combining 73 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were:

@@

\subsubsection{Data Type}
Irrespective with whom the data was shared or on what device, participants were most concerned about photos/videos, especially if they contain embarrassment, nudity, or financial information. Information which can be used to impersonate the user (i.e. username and password for websites) and invasions of privacy (photos of someone at home) were also considered to be sensitive data. Top and bottom absolute <data> rankings can be seen in Tables ~\ref{top10} and ~\ref{bottom10}. Generally, the most concerning and least concerning data types did not change by recipient. {\color{red} can be said for ~top/bottom5 looking at the recipient lists I commented out; but this isn't too official since we do no stat tests.}
